\bf On semidefinite-representable sets over valuation fields

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

\begin{remark}
  Assume $\val$ is a discrete valuation. Then if \eqref{LP} admits feasible vectors,
  $p^*$ is either $-\infty$ or attained at some solution $x^*$.
\end{remark}

>>>>

\begin{remark}
  Assume $\val$ is a discrete valuation. Then\footnote{\simone{Cela voudrait dire que
    si la valuation n'est pas discrète, on pourrait avoir un problème LP qui est admissible
    (c'est-à-dire l'ensemble admissible est non-vide) et où $p^* \in \ZZ$, mais $p^*$ n'est
  pas atteint. C'est ça ? A-t-on des exemples ?}} if \eqref{LP} admits feasible vectors,
  $p^*$ is either $-\infty$ or attained at some solution $x^*$.
\end{remark}
